---
title: "tesla3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

---
title: "Tesla Stock Price Forecasting"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
## Read the data file in R
data <- read.csv("~/Desktop/Time Series/TSLA.csv")
```

## Data Preprocessing
```{r}
library(dplyr)

##gives the first 6 rows
head(data)

## gives the format for each column and some sample data
str(data)  

data$Date<- strptime(as.POSIXct(data$Date,origin="1970-01-01 00:00.00"),"%Y-%m-%d")
data$Date <- as.factor(data$Date)

df_close<- data %>%
  group_by(Date)%>%
  summarise(Close=mean(Close, na.rm = TRUE))

df_close$Date <- as.Date(df_close$Date)
df_close <- as.data.frame(df_close)

row.names(df_close) <- df_close$Date

plot(df_close, ylab="Close Price Tesla", type="l")


```


```{r}

# removing days for future prediction
forecast_time=14
df_input <- head(df_close, -forecast_time)
df_test <- tail(df_close, forecast_time)
```

```{r}
# Creating time series for modeling and future comparing of prediction
input_ts <- ts(df_input$Close,start=c(2010,06,29),frequency=365)
test_ts <- ts(df_test$Close,start=end(input_ts)+c(0,1),frequency=365)
```

## Including Plots

```{r}
plot(input_ts, main="Original Stock Price", xlab = "Time", ylab = "Time", type = 'l')

## Differencing the Tesla stock prices and plotting it
diff.tesla=diff(input_ts)
plot(diff.tesla,type='l',main='Difference Tesla')


#Take log of original series and plot the log price
log.tesla=log(input_ts)
plot(log.tesla,type='l',main='Log Tesla')
# Differencing log price and plot
difflog.tesla=diff(log.tesla)
plot(difflog.tesla,type='l',main='Difference Log Tesla')
```



```{r}
#Performing grid arima analysis
p = c(0:5)
d = 1
q = c(0:5)

grid_arima <- function(input,p,d,q){
  aic_list <- list()
  combination = expand.grid(p,d,q)
  for (i in c(1:nrow(combination))){
    p_<- combination[i,1]
    d_<- combination[i,2]
    q_<- combination[i,3]
    fit <- arima(input, order = c(p_,d_,q_))
    name <- paste(p_,d_,q_)
    aic_list[name] <- fit$aic
  }
return(aic_list)
}

aic_d1<-data.frame(names(grid_arima(log(tesla.close),p,d,q)), unlist(cbind(grid_arima(log(tesla.close),p,d,q))) )
colnames(aic_d1)<- c("model","AIC")
```
```{r}
```


```{r}
head(aic_d1,10)
```
```{r}
subset(aic_d1, aic_d1$AIC %in% sort(aic_d1$AIC)[1:3])
```
```{r}
library(forecast)
library(TSA)
fit_arima <- auto.arima(input_ts, d = 1, D = 1, stepwise = FALSE, approximation = FALSE, trace = TRUE);
print(summary(fit_arima))
```



```{r}
library(forecast)
library(TSA)

close_arima <- auto.arima(input_ts)
close_arima_preds = close_arima %>% forecast(h= nrow(df_test)) %>% data.frame()
accuracy(close_arima_preds$Point.Forecast, test_ts)

close_arima_preds
{plot(close_arima_preds, main = expression("auto.ARIMA(1,0,3)(1,1,0)"[52]))
lines(ts(week_price))}
ts.plot(close_arima_preds$Lo.80, prediction, col=c("Black", "blue"), lty=c(1,3))
ts.plot(close_arima_preds$Hi.95, prediction, col=c("Black", "blue"), lty=c(1,3))
ts.plot(close_arima_preds$Lo.95, prediction, col=c("Black", "blue"), lty=c(1,3))
```


```
### Model Diagnostics

```{r}
tsdisplay(residuals(Arima_4_1_3), lag.max=45, main='(4,1,3) Model Residuals')
```
ACF and PACF do not have any significant lag, indicating ARIMA(4,1,3) is a good model to represent the series.

```{r}
 Box.test(resid(Arima_4_1_3),type="Ljung",lag=20,fitdf=0)

```
The test statistic of the test is 6.321 and the p-value of the test is 0.9984, which is much larger than 0.05. So we cannot reject the hypothesis that the autocorrelation is different from 0.Therefore, the selected model is an appropriate one of Apple stock price.


```{r}
tseries::kpss.test(diff(log(input_ts),lag=2), null="Level")
tseries::kpss.test(diff(log(input_ts),lag=2), null="Level")
tseries::adf.test(diff(log(input_ts),lag=2))
```


```{r}
Sarima_4_1_3 <- arima(log(input_ts), order= c(5,2,5), seasonal = list(order=c(1,2,0), period=2))
#performing prediction
model.predict = predict(Sarima_4_1_3, n.ahead = forecast_time)
# invert log transformation
prediction <- exp(model.predict$pred)
#calculating RMSE
model_rmse = sqrt(mean((test_ts - prediction)**2))
ts.plot(test_ts, prediction, col=c("Black", "blue"), lty=c(1,3))
```
```{r}
Sarima_4_1_3 <- arima(log(input_ts), order= c(5,2,5), seasonal = list(order=c(1,2,0), period=2))
#performing prediction
model.forecast = forecast(Sarima_4_1_3, n.ahead = forecast_time)
# invert log transformation
prediction <- exp(model.forecast$pred)
#calculating RMSE
model_rmse = sqrt(mean((test_ts - prediction)**2))
ts.plot(test_ts, prediction, col=c("Black", "blue"), lty=c(1,3))
```


 ARIMA is a method to linearly model, it provides best linear forecast for the series, and thus plays little role in forecasting model nonlinearly. To model volatility, ARCH/GARCH method comes into play.
